%Disclaimer


\chapter*{Disclaimer}\label{Disclaimer}


The information contained in this book (henceforth referred to as “text") is in no way financial or investment advice of any kind. 

All information presented in this text is meant for entertainment and educational purposes only. 

There is no endorsement or solicitation of any investment strategy or any specific investment contained within this text. 

No guarantee of returns is stated or implied by this text.

The author of this text does not give financial or investment advice of any kind.

The author author of this text is not a financial advisor, registered investment advisor, or broker-dealer. The author of this text holds no financial certifications or licenses, or any formal financial training of any kind whatsoever. 

Options are not suitable for everyone, and as such, should be discussed with a licensed professional prior to taking any action.

Any action taken by readers of this text is taken of their own volition, is solely their responsibility, and no fiduciary relationship is established between Call to FIRE, LLC or the author of this text and its readers. 

Although the aim of this text is to provide accurate information, no claims of veracity, accuracy, validity or being “up-to-date” are made or guaranteed. Call to FIRE LLC and the author of this text are not liable for any errors or omissions contained herein, and therefore the information contained herein should not be relied on for any financial decisions, or in any other way whatsoever. This text provides no warranties or guarantees whatsoever. Because you should not rely on this text in any way, any reliance on or utilization of information found on this text is at your own risk. As such, any and all actions taken with regard to financial and investing decisions should be researched by the individual investor, and said individual investor should seek consultation with an investment professional before taking any action.

All investments involve risk, including the possibility of loss. Understanding any strategy prior to implementation is the responsibility of the individual trader, and as such individuals assume full responsibility and accountability for all profits or losses they accrue. 

No warranties exist, express or implied. The author of this text disclaims to the fullest extent of the law any warranties assumed regarding this text and the material contained herein. 

No express or implied representation or guarantee of earnings and or returns gained from reading and engaging with this text, monetary or otherwise, are claimed by the author or Call to FIRE, LLC.

Call to FIRE LLC and the author of this text do not provide medical advice in any way, shape, or form. 

Call to FIRE LLC and this book's author expressly exclude liability for any consequences resulting from reading or engaging with this text. By engaging with this text you expressly acknowledge that this text and its author are exempt from any and all liability to losses, physical or otherwise, related to this text, its content, and results of engaging with it, or acting upon any information contained within.

You may reproduce content without permission for personal use only. 

If you wish to reproduce content for something other than personal use, express and written permission for each use must be obtained from Call to FIRE LLC and the author of this text, which details the manner (duration, venue, etc) in which it will be presented and used.

This book's author may share opinions of products, services, etc but makes no endorsements whatsoever. All opinions are entirely voluntary and entirely uncompensated.

Before you can trade options, you must read “Characteristics \& Risks of Standardized Options,” also known as the options\\ disclosure document (ODD), which is located at:\\
http://www.optionsclearing.com/
about/publications/\\publication-listing.jsp

\newpage

\begin{center}
    \vspace*{4cm}
    \Large
    This book contains cartoons of wizards and should not be taken seriously.
    
\end{center}

